### 2018-08-07 paper/evaluation.tex
minor eval git submodule update

\newcommand\tuser{\ensuremath{t_{\text{user}}}}
\newcommand\ndevices{\ensuremath{n_{\text{devices}}}}

@@

\paragraph*{File transfer} The main parameter here is the chunk size \chunksize, that was set to 512KB, which is considered, in BitTorrent, to be a good trade-off between network efficiency and number of chunks.
The other parameter, \tupload, was empirically set to 500ms.

\paragraph*{Users' behavior} Finally we set \tuser to 3s.

@@

\begin{figure}[t]
  \centering
  %\def\svgwidth{0.8\columnwidth}
  \includegraphics[width=\columnwidth]{figures/bw_and_pending_files_log.pdf}

  \caption{\label{fig:bw_and_pending_files_log}Traffic during one experiment.
  In gray: number of pending file exchanges; in black: mean outbound traffic (kB) per node per second.}
\end{figure}

>>>>

@@

\paragraph*{File transfer} The main parameter here is the chunk size \chunksize, that was set to 512KB, which is considered, in BitTorrent, to be a good trade-off between network efficiency and number of chunks.
The other parameter, \tupload, that is the period between two chunk sends, was empirically set to 500ms.

\paragraph*{Users' behavior} We set \tuser, the time between two user actions, to 3s.

@@
